The Design and Implementation of the Synchronous Language \CEU

### 2016-09-30 paper.tex
(>) overly complex semantics

Despite its success and influence, Esterel has a complex semantics that
requires careful static analysis to detect and refuse programs with 
\emph{causality} and \emph{schizophrenia} problems%
%These problems have an extensive coverage in the literature 
~\cite{esterel.constructive,esterel.d7,esterel.d6,esterel.d3,esterel.d5,esterel.d8,esterel.d1,esterel.schizo2}.
%
A complex semantics not only challenges the analysis and compilation of 
programs, but also results in incompatible and non-compliant implementations.
%
Above all, it also affects the programmer's understanding about the code, 
who, ultimately, has to solve the errors when facing corner cases.
%
Another drawback of the Esterel semantics consists of non-deterministic
execution for intra-reaction statements.
Non determinism prevents threads from interacting with stateful system calls safely 
and makes shared-memory concurrency not as straightforward as reading and 
writing to shared variables.
%
%For instance, although Esterel supports orthogonal abortion of 
%threads~\cite{esterel.preemption}, it doesn't offer an effective mechanism to 
%release resources in use.

>>>>

Despite its success and influence, Esterel has a complex semantics that
requires careful static analysis to detect and refuse programs with 
\emph{causality} and \emph{schizophrenia} problems%
%These problems have an extensive coverage in the literature 
~\cite{esterel.constructive,esterel.d7,esterel.d6,esterel.d3,esterel.d5,esterel.d8,esterel.d1,esterel.schizo2}.
%
A complex semantics not only challenges the analysis and compilation of 
programs, but also affects the programmer's understanding about the code, who,
ultimately, has to solve the errors when facing corner cases.
%
Another drawback of the Esterel semantics consists of non-deterministic
execution for intra-reaction statements.
Non determinism prevents threads from interacting with stateful system calls safely 
and makes shared-memory concurrency not as straightforward as reading and 
writing to shared variables.
%
%For instance, although Esterel supports orthogonal abortion of 
%threads~\cite{esterel.preemption}, it doesn't offer an effective mechanism to 
%release resources in use.
